%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {AI Engineer} % Job title
    {Armakuni} % Organization
    {Remote} % Location
    {Mar. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Smart Call Assistant:} Developed AI-powered call assistant integrating \textbf{ElevenLabs TTS}, \textbf{AWS Transcribe STT}, \textbf{Amazon Bedrock LLM}, and \textbf{OpenSearch} for knowledge base. Implemented features for Google Calendar booking, availability lookup, and real estate broker website building.
        \vspace{0.4em}
        \item \textbf{Medical RAG SMS Chatbot:} Built medical domain RAG chatbot using \textbf{Twilio} with comprehensive issue escalation, tracking, and follow-up capabilities for healthcare communication.
        \vspace{0.4em}
        \item \textbf{Gaming Character Generation:} Created text-to-image and image-to-image generation system for consistent character creation in gaming industry using \textbf{SageMaker}, \textbf{ComfyUI}, and \textbf{Qwen image edit models}.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {DosePack (Meditab)} % Organization
    {Ahmedabad} % Location
    {Dec. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{API Development:} Designed and implemented RESTful APIs to streamline business workflows, reduce response times by 50\%, and enhance system interoperability.
        \vspace{0.4em}
        \item \textbf{Migration Automation:} Automated database migration processes, reducing deployment time by 40\% with version control across environments. Created and published PyPi library for the same.
        \item \textbf{Data Engineering and Analytics:} Built ETL pipelines for \textbf{ data pre-processing, feature engineering and validation} to support analytics. created daily performance statics for stakeholders 
        \vspace{0.4em}
        \item \textbf{Real-time Systems:} Developed real-time solutions using \textbf{WebSockets}, enabling bi-directional communication for features like \textbf{live updates}, \textbf{dynamic dashboards}, and \textbf{notification services}.
        \vspace{0.4em}
        \item \textbf{Authentication Systems:} Designed and implemented secure authentication systems using token-based mechanisms \textbf{(JWT)} and role-based access control \textbf{(RBAC)}. Developed a seamless single sign-on \textbf{(SSO)} solution with \textbf{OAuth2.0 scopes}.
        \vspace{0.4em}
        \item \textbf{Database Engineering:} Enhanced backend performance by designing a well-optimized SQL database, significantly improving storage utilization and system efficiency.
        \vspace{0.4em}
        \item \textbf{Algorithm Optimization:} Optimized computationally intensive algorithms for \textbf{pack-filling slot customizations} and workflow optimizations.
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
