%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}



%---------------------------------------------------------
 \begin{itemize}
 \item \textbf{High-Performance Packet Processor: } Built a multi-threaded packet processing engine in C++ using DPDK for high-speed network traffic analysis. Implemented TCP/UDP packet parsing, flow classification, and basic firewall rules with zero-copy packet handling achieving 10Gbps throughput.
 \item \textbf{Software-Defined Network Controller: } Developed an SDN controller in GoLang that manages virtual network topologies and routing policies. Implemented OpenFlow protocol support for dynamic flow table management and network virtualization with REST APIs for network configuration.
 \item \textbf{Stable Diffusion: } Developed a project using Stable Diffusion models to generate images. Gained hands-on experience in generative AI concepts, including LORAs, VAEs, CUDA and checkpoints, enhancing my understanding of image generation workflows and model fine-tuning. This project deepened my knowledge generative AI techniques.
 \item \textbf{Consistent Character Generator: } Text-to-image and image-to-image system for consistent character creation using SageMaker, ComfyUI, and Qwen models. used LoRAs and quantized models to reduce processing time
 \item \textbf{Distributed Load Balancer: } Created a fault-tolerant load balancer using C++ and Python with health checking, session persistence, and automatic failover. Implemented consistent hashing for traffic distribution across multiple backend servers with real-time metrics collection.
 \item \textbf{Medical RAG SMS Chatbot: } Healthcare chatbot using Twilio with issue escalation, tracking, and follow-up capabilities.
 \item \textbf{Network Monitoring Dashboard: } Built a real-time network monitoring system using Python and WebSockets that tracks bandwidth utilization, packet loss, and latency metrics. Integrated with Grafana for visualization and alerting on network anomalies.
 \item \textbf{Smart Call Assistant: } AI-powered call system with ElevenLabs TTS, AWS Transcribe STT, Bedrock LLM, and OpenSearch. Features Google Calendar booking and real estate tools.
 \item  \textbf{AI Movie Recommendation: }movie recommendation using opensource GenAI APIs.

 \end{itemize}
%---------------------------------------------------------


\end{cventries}
